Testing Methodologies for Asynchronous Centralized Simulations\\

### 2020-12-04 paper/PaperDraft2.tex
Verbiage change
Almost the last paper changes

Putting all of these features together, we have arrived at all of the tools necessary to build the framework to the state in which it can automatically start a game instance, control a player, 
and ultimately verify the game across all instances. The reader is encouraged to download and inspect the Testing Framework for the exact implementation of how instances are set up,
how assertions are defined how all of these are coupled in an asynchronous manner. Fig. 13 showcases 18 separate test cases which passed and were invoked automatically. As mentioned 
earlier, we thought it prudent to also visually show any changes should the user chose to perform a visual inspection. Likewise, the user also has the ability to manually invoke
any individual test case.

@@

>>>>

Putting all of these features together, we have arrived at all of the tools necessary to build the framework to the state in which it can automatically start a game instance, control a player, 
and ultimately verify the game across all instances. The reader is encouraged to download and inspect the Testing Framework for the exact implementation of how instances are set up,
how assertions are defined how all of these are coupled in an asynchronous manner. Fig. 13 showcases 18 separate passing test cases which were invoked automatically performed on 4 distinct instances.
As mentioned earlier, we thought it prudent to also visually show any changes should the user chose to perform a visual inspection. Likewise, the user also has the ability to manually invoke
any individual test case.

@@

\subsection{AutomatedFull-stack Testing}

Refering back to the implementation, we have an incentive to also test the entire stack. In order to provide access to the server, we proposed another interface from the Testing Framework
to the server in order to pull the internal state of the simulation. However, for this type of testing to be meaningful, we cannot simply start seperate instances of NodeTank and then immediately 
verify the state. To fully leverage this type of testing, we must have a mechanism by which to perform changes to the game from each instance for some amount of time before the actual comparison 
between clients and server may take place.

Firstly, we may build off of the framework we've developed for client-side testing as it has already solved the problem of programatically controlling a client in isolation and verifying the internal
state of a client. With the goal of applying a change of state to all clients, we have the solution of applying a random movement, shooting a random target, and a random shooting interval
for each client. These random events are generated again after a random amount of time, until the total amount of elapsed time reaches an upper bound in seconds, with all of these actions encompasing a "tick".
A random number of ticks are performed up to a certain upper bound, and after all ticks are executed, we may then fetch the internal state of the server and verify it against all instances.

\begin{lstlisting}[language=JavaScript,caption={Snippet of Invoking a Random Number of Automatic Tests}]
        let startTests = () => {
        currentTick = 0;
        currentMaxTicks = randomInRange(ticksBetweenChecks) + 1;
        runTest = true;
        resetAllCells();
        clearMessages();
        setInterval(() => {
            runIteration()
        }, tickLength * 1000);

        runIteration();
    };
\end{lstlisting}

Listing 4 showcases how each tick is invoked. Firstly, the initial values of our tracking variables are set, however lines 11 and 15 are of interest. Line 11 again uses a subset of the callback pattern
to asyncronously call the "runIteration" function after each tick length expires, and line 15 invokes the function immediatetly so that we do not have to wait for the tickLength to pass before the first
test case is kicked off.

\begin{lstlisting}[language=JavaScript,caption={Snippet of runIteration}]
    let runIteration = () => {
        if (runTest) {
            console.log("Tick " + currentTick);
            currentTick++;
            stopAllMovement();
            stopAllActions();
            t.setRandomMovement(gameInstance1);
            gameInstance1.messageObj.queuedText = messageSet[randomInRange(messageSet.length - 1)];

            //set each instance to shoot at another random instance
            interval1 = setInterval(() => {
                //aim at something other than itself
                let target = 0;
                while (target === 0) {
                    target = randomInRange(3);
                }
                gameInstance1.playerTank.setLookAt(instanceArray[target].playerTank.group.position);
                gameInstance1.clicked = true;

                stopAllMovement();
                t.setRandomMovement(gameInstance1);
            }, randomInRange(tickLength) * 1000);
\end{lstlisting}

Finally,
